
```{r}
#| echo: false
source('../Code/libraries.r')
source("../Code/ProcessRawData.r")
source("../Code/FitModels.r")
sp500=ProcessRawData()
```

```{r}
#| echo: false
Result=FitModels(Model="GARCH11",Data=sp500,)
omega=coef(Result)['omega']
alpha=coef(Result)['alpha1']
beta=coef(Result)['beta1']
LogLikelihood = likelihood(Result)  
```

## Data

We are analysing SP-500 returns from `r min(sp500$date.ts)` to `r max(sp500$date.ts)`, `r length(sp500$date.ts)` observations. If you like thousand commas in your numbers, then  `r prettyNum(length(sp500$date.ts), big.mark = ",")` observations.

```{r}
#| echo: false
plot(sp500$price.ts,
 lwd=2,
 col='blue',
 las=1,
 bty='l',
 xlab="day",
 ylab='price',
 main="The SP-500 index",
)
```

## Analysis of SP-500 volatility

When we estimate a GARCH(1,1), we get these parameters

```{r}
#| echo: false
knitr::kable(Result@fit$matcoef)
```

Note that since alpha+beta=`r round(alpha+beta,2)`<1 , the model is covariance stationary.


Note that since $\alpha+\beta=`r round(alpha+beta,2)`<1$ , the model is covariance stationary.

The Log Likelihood is `r prettyNum(LogLikelihood, big.mark = ",")` .

### Returns with 2 times volatility

```{r}
#| echo: false

plot(Result,which=1)
```

## Some VaR analysis

```{r}
Portfolio = 1000
sigma = 0.01
p = 0.05
VaR = -qnorm(p) * Portfolio * sigma
```

Risk is \$`r round(VaR,1)` according to the VaR.
